%----------HEADING-----------------
\ContactInfo{Rick Daalhuizen}{rick.daalhuizen@outlook.com}{Antwerp, Belgium}{+32-495-499-157}
\noindent\href{https://www.linkedin.com/in/rickdaalhuizen90}{www.linkedin.com/in/rickdaalhuizen90}

%-----------PROFILE-----------------
\section{Profile}
Senior Backend Developer with 7+ years of experience in PHP, backend development, and system architecture. Skilled in building scalable APIs, optimizing performance, and troubleshooting under pressure. Known for clear communication and a practical approach, delivering results that matter.

%-----------EXPERIENCE-----------------
\section{Experience}
\ListStart

  \item
  \JobEntry{Independent Contractor}{Self-Employed / Remote}{Back End Developer}{Sept. 2024 -- Present}
  \SubListStart
    \BulletItem{Managed the full lifecycle for an Adobe Commerce marketplace extension, from requirements to deployment.}
    \BulletItem{Automated environment setup and testing workflows, improving reliability and reducing deployment risks.}
    \BulletItem{Integrated Cypress and MFTF tests into CI pipelines to streamline quality assurance.}
    \BulletItem{Produced technical documentation and user guides to support onboarding and troubleshooting.}
    \BulletItem{Expanded technical expertise by learning C and x86 assembly for deeper system understanding.}
  \SubListEnd

  \item
  \JobEntry{MaxServ}{Waalwijk, Netherlands}{Back End Developer (PHP)}{Apr. 2022 -- Sept. 2024}
  \SubListStart
    \BulletItem{Connected e-commerce platforms with enterprise systems (SAP, ERP, PIM) through API development and database management.}
    \BulletItem{Designed asynchronous systems with RabbitMQ and optimized caching with Redis and Varnish, achieving 45\% faster load times and 99.98\% uptime during peak sales.}
    \BulletItem{Improved performance and scalability for high-traffic sites.}
    \BulletItem{Contributed to code review, unit testing, and agile project delivery.}
    \BulletItem{Used analytics tools for rapid issue resolution and minimal downtime.}
    \BulletItem{Developed documentation and training materials to standardize processes.}
  \SubListEnd

  \item
  \JobEntry{Endriven}{Enschede, Netherlands}{Full-stack Developer (PHP + React)}{Oct. 2021 -- Apr. 2022}
  \SubListStart
    \BulletItem{Developed and maintained integrations for Magento 2 and Symfony using industry standards.}
    \BulletItem{Built frontends with ReactJS and integrated backend services via GraphQL APIs.}
    \BulletItem{Applied design patterns and agile methods for maintainable, scalable solutions.}
    \BulletItem{Participated in code review, unit testing, and debugging.}
    \BulletItem{Collaborated with stakeholders to deliver projects on time and to specification.}
  \SubListEnd

  \item
  \JobEntry{Webelephant}{Breda, Netherlands}{Back End Developer (PHP)}{Aug. 2018 -- Sept. 2021}
  \SubListStart
    \BulletItem{Led backend migration of a large e-commerce platform (100,000+ users) to a modern architecture with zero downtime.}
    \BulletItem{Designed and implemented RESTful APIs for order and product synchronization with marketplaces (Amazon, Bol.com).}
    \BulletItem{Established containerization best practices for faster, more reliable deployments.}
    \BulletItem{Standardized documentation for APIs and migration processes, improving onboarding.}
  \SubListEnd

\ListEnd

%--------CERTIFICATIONS------------
\section{Certifications}
\ListStart
  \item
  \JobEntry{Adobe Commerce Professional Developer}{AD0-E724}{Expertise in implementing and managing Adobe Commerce solutions.}{Mar. 2022}
\ListEnd

%-----------EDUCATION-----------------
\section{Education}
\ListStart
  \item
  \JobEntry{KdG University of Applied Sciences and Arts}{Antwerp, Belgium}{Bachelor of Applied Science (BASc), Applied Computer Science (Evening)}{Sept. 2022 -- Jan. 2024}

  \item
  \JobEntry{ROC Da Vinci College}{Dordrecht, Netherlands}{Secondary Vocational Education, Software Development}{2015 -- 2018}
\ListEnd

%--------SKILLS------------
\section{Skills}
\ListStart
  \DetailItem{Programming Languages}{PHP, JavaScript, TypeScript, React, SQL, XML, HTML/CSS}
  \DetailItem{Frameworks/Technologies}{REST/GraphQL APIs, MySQL, Redis, RabbitMQ, Varnish, Docker, Kubernetes, CI/CD, Git, AWS, Magento, Symfony, Zend}
  \DetailItem{Development Practises}{Agile methodologies, project management, code review, unit testing, debugging, requirements analysis, DevOps}
  \DetailItem{System Architecture}{Microservices, performance optimization, scalability, system architecture}
  \DetailItem{Soft Skills}{Problem-solving, troubleshooting, communication, working under pressure, mentoring, documentation, team delivery}
\ListEnd

%--------INTERESTS------------
\section{Interests}
\ListStart
  \DetailItem{Pursuits}{Creative writing, side projects, sports, and outdoor activities}
  \DetailItem{Languages}{Fluent in Dutch and English}
\ListEnd
