% English Content

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Rick Daalhuizen} & E-mail : \href{mailto:rick.daalhuizen@outlook.com}{rick.daalhuizen@outlook.com}\\
   & Phone : +32-495-499-157 \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Upvado}{Antwerp, Belgium}
      {Freelancer - Software Developer}{Sept. 2024 - Present}
      \resumeItemListStart
        \resumeItem{Adobe Commerce}
          {Successfully developed and published Adobe Commerce extensions, compliant with marketplace quality standards.}
        \resumeItem{Shopify}
          {Developed a Shopify app for sending SMS messages for abandoned carts.}
      \resumeItemListEnd
  
    \resumeSubheading
      {MaxServ}{Waalwijk, Netherlands}
      {Backend Developer (PHP)}{Apr. 2022 - Sept. 2024}
      \resumeItemListStart
        \resumeItem{Adobe Commerce Integration}
          {Integrated and developed Adobe Commerce (Magento) modules with SAP, ERP, POS, and PIM (Akeneo) systems using Docker, Kubernetes.}
        \resumeItem{Performance Optimization}
          {Optimized store performance by implementing RabbitMQ for asynchronous processing, resolving bottlenecks with XDebug, and leveraging Redis and Varnish caching for improved page speed.}
        \resumeItem{Remote Team Collaboration}
          {Experience in remote collaboration and self-management in a distributed team. Utilized SCRUM and Jira for agile project management, delivering solutions on time.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Endriven}{Enschede, Netherlands}
      {Full-stack Developer (PHP + React)}{Oct. 2021 - Apr. 2022}
      \resumeItemListStart
        \resumeItem{Magento 2 \& Shopware}
          {Developing and integrating modules for Magento 2 and Shopware, including PIM integrations such as Pimcore.}
        \resumeItem{Frontend Development}
          {Experience building front-ends with Vue.js and GraphQL for interactive websites.}
      \resumeItemListEnd

    \resumeSubheading
      {Webelephant}{Breda, Netherlands}
      {Back-end Developer (PHP)}{Aug. 2018 - Sept. 2021}
      \resumeItemListStart
        \resumeItem{Magento 1 to 2 Migration}
          {Worked on large-scale sites like Skiwebshop, and assisted in migrating Magento 1 stores to Magento 2.}
        \resumeItem{API Integration}
          {Implemented RESTful APIs to integrate with platforms like Amazon, Bol.com, and Admarkt.}
        \resumeItem{Headless Commerce}
          {Migrated e-commerce shops to headless implementations using ScandiPWA and ReactJS.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd

%--------CERTIFICATIONS------------
\section{Certifications}
  \resumeSubHeadingListStart
    \resumeSubItem{Adobe Commerce Professional Certification}
      {Certified in [March, 2022]. Demonstrates expertise in implementing and managing Adobe Commerce solutions.}
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {KdG University of Applied Sciences and Arts}{Antwerp, Belgium}
      {Bachelor of Applied Science (BASc), Applied Computer Science (Evening)}{Sept. 2022 -- Jan. 2024}
      \resumeItemListStart
        \resumeItem{Courses}
          {Built a solid foundation in software development, data structures, and algorithms, and created a game with Java FX.}
      \resumeItemListEnd
      
    \resumeSubheading
      {ROC Da Vinci College}{Dordrecht, Netherlands}
      {Secondary vocational education, Software Development}{2015 - 2018}
      \resumeItemListStart
        \resumeItem{Courses}
          {Focused on web/mobile development with PHP, SQL, JavaScript, and security practices including ethical hacking.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Core Technologies}{: PHP, Adobe Commerce (Magento), RabbitMQ, XDebug, Redis, GraphQL, REST, XML, SQL, Docker, Kubernetes, CI/CD, Automated testing, Akeneo, SAP, ERP}
   }
   \item{
     \textbf{Other Technologies}{: Java, Python, Javascript, HTML, CSS}
   }
 \resumeSubHeadingListEnd

%--------INTERESTS------------
\section{Interests}
 \resumeSubHeadingListStart
   \item{
     \textbf{Hobbies}{: Programming, open-source contributions, reading, sport, and travel.}
   }
   \item{
     \textbf{Languages}{: Fluent in Dutch and English}
   }
 \resumeSubHeadingListEnd
